---
title: "CVS DD IRR 2020-07-17"
author: "Marsha"
date: "07/17/2020"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
    depth: 3
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(irr)
library(dplyr)
library(tidyverse)
```

# Example
## Krippendorff's Alpha example from R documentation
```{r eval = TRUE, message = FALSE}
nmm<-matrix(c(1,1,NA,1,2,2,3,2,3,3,3,3,3,3,3,3,2,2,2,2,1,2,3,4,4,4,4,4,
              1,1,2,1,2,2,2,2,NA,5,5,5,NA,NA,1,1,NA,NA,3,NA),nrow=4)
# first assume the default nominal classification
kanom<-kripp.alpha(nmm)
view(kanom)
# now use the same data with the other three methods
kaordinal<-kripp.alpha(nmm,"ordinal")
kaint<- kripp.alpha(nmm,"interval")
karat<- kripp.alpha(nmm,"ratio") 
```

# Importing Data
## Importing data csv from local file 
```{r eval = TRUE, message = FALSE}
rm(list=ls()) 
graphics.off()
getwd()
setwd('C:/Users/Marsha/Box/CVS Beverage Tax/CVS Data Coding/Double Data Entry/200 Entries MT Data')
data <- read.csv('200_entries_combined_mt.csv')
```






# Bev Type Category
## Transmuting data into new table with just the grocery category and dd
```{r eval = TRUE, message = FALSE}
type<- transmute(data, type_mt = data$beverage_type_mt, type_ra = data$beverage_type_ra)
```

## Recoding all categories into numeric and standardizing
```{r eval = TRUE, message = FALSE}
table(type$type_mt)
table(type$type_ra)
#Relabel values for type, unsure and bev not found together
# beverage not found 1
#coffee 2
#concentrates 3
#energy drink 4
#flavored water 5
#iced tea or lemonade 6
#juice 7
#milk 8
#milk alternative 9
#not a beverage 10
#other beverage 11
#regular water 12
#soda 13
#sparkling water 14
#sports drink 15
# unsure 1

#Relabel values for type

type <- mutate(type, type_mt=factor(type_mt, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
type <- mutate(type, type_ra=factor(type_ra, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
```

## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
type_tp <- t(type)
```

## Krippendorf's alpha for beverage type
```{r eval = TRUE, message = FALSE}
k_type <- kripp.alpha(type_tp, "nominal")
#view(k_type)
#k_grocery_drop <- kripp.alpha(grocery_tp_drop, "nominal")
#view(k_grocery_drop)
print("K Alpha Beverage Type")
k_type
#k_grocery_drop
#Agreement for grocery category is 0.961 for 4889 subjects with 2 raters. 
#Agreement is 0.951 for 3858 subjects with 2 raters, with double restaurant determination dropped (n=1031)
```



# Sweetener Category
## Transmuting data into new table with just the sweetener and dd
```{r eval = TRUE, message = FALSE}
sweet<- transmute(data, sweet_mt = data$sweetener_type_mt, sweet_ra = data$sweetener_type_ra)
```

## Recoding all categories into numeric and standardizing
```{r eval = TRUE, message = FALSE}
table(sweet$sweet_mt)
table(sweet$sweet_ra)
#Relabel values for type, unsure and bev not found together
# artificial 1 
# hybrid 2
# not sweetened 3
# sugar 4
# sweetened (unknown) 5
# unknown 6


#Relabel values for type

sweet <- mutate(sweet, sweet_mt=factor(sweet_mt, levels = c("artificial", "hybrid", "not sweetened", "sugar", "sweetened (unknown)", "unknown"),
                                                 labels = c(1, 2, 3, 4, 5, 6)))
sweet <- mutate(sweet, sweet_ra=factor(sweet_ra, levels = c("artificial", "hybrid", "not sweetened", "sugar", "sweetened (unknown)", "unknown"),
                                                 labels = c(1, 2, 3, 4, 5, 6)))
```

## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
sweet_tp <- t(sweet)
```

## Krippendorf's alpha for beverage sweet
```{r eval = TRUE, message = FALSE}
k_sweet <- kripp.alpha(sweet_tp, "nominal")
#view(k_sweet)
#k_grocery_drop <- kripp.alpha(grocery_tp_drop, "nominal")
#view(k_grocery_drop)
print("K Alpha Sweetener")
k_sweet
#k_grocery_drop
#Agreement for grocery category is 0.961 for 4889 subjects with 2 raters. 
#Agreement is 0.951 for 3858 subjects with 2 raters, with double restaurant determination dropped (n=1031)
```

# Tax Category
## Transmuting data into new table with just the tax and dd
```{r eval = TRUE, message = FALSE}
tax <- transmute(data, tax_mt = data$tax_status_mt, tax_ra = data$tax_status_ra)
```

## Recoding all categories into numeric and standardizing
```{r eval = TRUE, message = FALSE}
table(tax$tax_mt)
table(tax$tax_ra)
#Relabel values for tax, unsure and bev not found together
# not taxed 1
# taxed 2
# unsure 3

#Relabel values for tax

tax <- mutate(tax, tax_mt=factor(tax_mt, levels = c("not taxed", "taxed", "unsure"),
                                                 labels = c(1, 2, 3)))
tax <- mutate(tax, tax_ra=factor(tax_ra, levels = c("not taxed", "taxed", "unsure"),
                                                 labels = c(1, 2, 3)))
```

## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
tax_tp <- t(tax)
```

## Krippendorf's alpha for beverage tax
```{r eval = TRUE, message = FALSE}
k_tax <- kripp.alpha(tax_tp, "nominal")
#view(k_tax)
#k_grocery_drop <- kripp.alpha(grocery_tp_drop, "nominal")
#view(k_grocery_drop)
print("K Alpha Tax")
k_tax
#k_grocery_drop
#Agreement for grocery category is 0.961 for 4889 subjects with 2 raters. 
#Agreement is 0.951 for 3858 subjects with 2 raters, with double restaurant determination dropped (n=1031)
```













# Individual Rater Checks
# 1 - Andres
```{r eval = TRUE, message = FALSE}
type1<- filter(data, data$ra_name.1 == "Andres")
type1<- transmute(type1, type_mt = type1$beverage_type_mt, type_ra = type1$beverage_type_ra)
```

## Recoding all categories into numeric and standardizing
```{r eval = TRUE, message = FALSE}
type1 <- mutate(type1, type_mt=factor(type_mt, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
type1 <- mutate(type1, type_ra=factor(type_ra, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
```
## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
type1_tp <- t(type1)
```
## Krippendorf's alpha for beverage type
```{r eval = TRUE, message = FALSE}
k_type1 <- kripp.alpha(type1_tp, "nominal")
print("K Alpha - Andres")
k_type1
```

# Individual Rater Checks
# 2 - Frid
```{r eval = TRUE, message = FALSE}
type2<- filter(data, data$ra_name.1 == "Frid")
type2<- transmute(type2, type_mt = type2$beverage_type_mt, type_ra = type2$beverage_type_ra)
```

## Recoding all categories into numeric and standardizing
```{r eval = TRUE, message = FALSE}
type2 <- mutate(type2, type_mt=factor(type_mt, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
type2 <- mutate(type2, type_ra=factor(type_ra, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
```

## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
type2_tp <- t(type2)
```

## Krippendorf's alpha for beverage type
```{r eval = TRUE, message = FALSE}
k_type2 <- kripp.alpha(type2_tp, "nominal")
print("K Alpha - Frid")
k_type2
```


# Individual Rater Checks
# 3 - Lubbers
```{r eval = TRUE, message = FALSE}
type3<- filter(data, data$ra_name.1 == "Lubbers")
type3<- transmute(type3, type_mt = type3$beverage_type_mt, type_ra = type3$beverage_type_ra)
```

## Recoding all categories into numeric and standardizing
```{r eval = TRUE, message = FALSE}
type3 <- mutate(type3, type_mt=factor(type_mt, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
type3 <- mutate(type3, type_ra=factor(type_ra, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
```

## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
type3_tp <- t(type3)
```

## Krippendorf's alpha for beverage type
```{r eval = TRUE, message = FALSE}
k_type3 <- kripp.alpha(type3_tp, "nominal")
print("K Alpha - Lubbers")
k_type3
```

# Individual Rater Checks
# 4 - McKeown
```{r eval = TRUE, message = FALSE}
type4<- filter(data, data$ra_name.1 == "McKeown")
type4<- transmute(type4, type_mt = type4$beverage_type_mt, type_ra = type4$beverage_type_ra)
```

## Recoding all categories into numeric and standardizing
```{r eval = TRUE, message = FALSE}
type4 <- mutate(type4, type_mt=factor(type_mt, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
type4 <- mutate(type4, type_ra=factor(type_ra, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
```

## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
type4_tp <- t(type4)
```

## Krippendorf's alpha for beverage type
```{r eval = TRUE, message = FALSE}
k_type4 <- kripp.alpha(type4_tp, "nominal")
print("K Alpha - McKeown")
k_type4
```

# Individual Rater Checks
# 5 - White
```{r eval = TRUE, message = FALSE}
type5<- filter(data, data$ra_name.1 == "White")
type5<- transmute(type5, type_mt = type5$beverage_type_mt, type_ra = type5$beverage_type_ra)
```

## Recoding all categories into numeric and standardizing
```{r eval = TRUE, message = FALSE}
type5 <- mutate(type5, type_mt=factor(type_mt, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
type5 <- mutate(type5, type_ra=factor(type_ra, levels = c("beverage not found", "coffee", "concentrates", "energy drink", "flavored water", "iced tea or lemonade",
                                                        "juice", "milk", "milk alternative", "not a beverage", "other beverage", "regular water", "soda", "sparkling water", 
                                                        "sports drink", "unsure"),
                                                 labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 1)))
```

## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
type5_tp <- t(type5)
```

## Krippendorf's alpha for beverage type
```{r eval = TRUE, message = FALSE}
k_type5 <- kripp.alpha(type5_tp, "nominal")
print("K Alpha - White")
k_type5
```

























# Checkin KCals
## Transmuting data into new table with just the kcals and dd
```{r eval = TRUE, message = FALSE}
kcal <- filter(data, data$Kcal_per_serving_1 > 0)
kcal <- transmute(kcal, kcal_mt = kcal$Kcal_per_serving_1, kcal_ra = kcal$Kcal_per_serving_2)
```


## Transposing data
```{r eval = TRUE, message = FALSE}
#subjects and raters were flipped so transposing the data using t() function
kcal_tp <- t(kcal)
```

## Krippendorf's alpha for beverage type
```{r eval = TRUE, message = FALSE}
k_kcal <- kripp.alpha(kcal_tp, "nominal")
print("K Alpha - kcal")
k_kcal
```





